---
title: "SRDBV5-ESSD"
output: html_document
---

```{r preliminaries, message=FALSE, echo=FALSE}
package_list <- c("cowplot","data.table","dplyr","ggplot2", "lubridate", "leaflet"
                  ,"kableExtra","knitr","ggmap","maps","mapdata","tidyr","sp","ggpubr")
# install.packages("styler")
package_new <- package_list[!(package_list %in% installed.packages()[,"Package"])]
if(length(package_new)) install.packages(package_new)
# loading necessary packages
# install.packages("xlsx")
# library("xlsx")
# install.packages("readxl")
library(readxl)
library(styler)
library(ggplot2)
theme_set(theme_bw())
library(cowplot)
library(tidyr)
library(dplyr)
library(cowplot)
library(data.table)
library(lubridate)
library(kableExtra)
library(knitr)
library(ggpubr)
library(ggmap)
library(maps)
library(mapdata)
library(leaflet)
library(sp)
# Source all needed functions
source('functions.R')

# set data and outputs file direction
DATA_DIR <- 'data'
OUT_DIR <- 'outputs'

# Set chunks defaults; these options will be applied to all subsequent chunks
knitr::opts_chunk$set(results = 'hide', message = TRUE, include = TRUE, 
                      echo = FALSE, warning = FALSE,
                      fig.height = 4, fig.width = 8, cache = FALSE)
```

# functions
```{r functions}
# input csv data
read_file <- function(x) read.csv(file.path(DATA_DIR, x), comment.char = "#", stringsAsFactors = FALSE)
# input xlsx data
# don't know why this function not work
# read_xlsx <- function(x) read.xlsx2(file.path(DATA_DIR, x), sheetIndex = 1, colIndex = c(1:4)) 
read_xlsx <- function(x) read_excel(file.path(DATA_DIR, x), sheet = 1)
# write csv 
writ_file <- function(input, output) write.csv(input, file.path(OUT_DIR, output), row.names = FALSE)
```

# load data
```{r load data}
# load all data necessary for this analysis
srdbv4 <- read_file('srdbv4.csv') 
srdbv5 <- read_file('srdb-data-v5.csv')
srdbv5$Site_ID <- as.factor(srdbv5$Site_ID)
IGBP <- read_file('IGBP.txt') %>% 
  left_join(read_file("igbp_mapping.csv"), by = "IGBP2001Pr")
# load global climate data (University of Delaware)
GlobalMATMAP <- read_file('summarized_climate.csv')
srdb_citation <- read_xlsx('SRDB_cited.xlsx')
MGRsD <- read_file('MGRsD.csv')
```


## Check the duplicate Site_ID in srdb
```{r}
# Idealy, every row in srdbv5 should have a unique ID (which is the combine of study_number, measure_year, and site_ID)
srdbv5 %>% 
  select(Study_number, Study_midyear, Site_ID) %>% 
  count(Study_number, Study_midyear, Site_ID, sort = TRUE) %>% 
  filter (n >= 2) %>% 
  arrange(Study_number)
```


# analysis
## srdb citation analysis
```{r}
srdb_citation %>% 
  select(PubYear, Num_citation, Database) %>%  
  ggplot(aes(PubYear, fill = Database)) +
  geom_bar(stat = "count") +
  scale_x_continuous(breaks = seq(2010, 2020, 2)) +
  labs(x=expression(Year), y=expression(Count))

ggsave('outputs/srdb_citation.jpg', width = 8, height = 5)
```


```{r}
# prepare data for legend
# cc_legend <- tibble(x = rep(-170, 3), 
#                     y = c(-25, -40, -55),
#                     size = c(1.25, 1.25, 1.25))
# Base map - word map
worldMap <- map_data(map = "world")
sitemap <- ggplot(data = worldMap) + 
  # geom_polygon(aes(x = long, y = lat , fill = region , group = group, alpha = 0.1), color = "white") + 
  geom_polygon(aes(x = long, y = lat, group = group, alpha = 0.1), color = "white", fill = "lightblue") + 
  coord_fixed(1.3) +
  theme(axis.text.y   = element_text(size = 12),
        axis.text.x   = element_text(size = 12),
        axis.title.y   = element_text(size = 13, margin = margin(t = 0, r = 12, b = 0, l = 0)),
        axis.title.x   = element_text(size = 13, margin = margin(t = 12, r = 0, b = 0, l = 0)),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        panel.border = element_rect(colour = "black", fill = NA, size = 1.25))+
  theme(legend.position = "none")+
  scale_x_continuous(name = "Longitude", breaks = seq(-180, 180, 30),
                     labels = seq(-180, 180, 30)) +
  scale_y_continuous(name = "Latitude", limits = c(-60, 90), breaks = seq(-90, 90, 15),
                     labels = seq(-90,90,15))

# add srdb-v4 sites
# RC sites from SRDB_v4
srdbv4 %>% 
  select(Latitude, Longitude) %>% 
  na.omit() %>% 
  count(Latitude, Longitude) ->
  srdbv4_count

# srdbv4_count$n %>% sort(decreasing = T)
# change count number > 10 to 10
srdbv4_count %>% 
  mutate(n2 = ifelse(n>=10, 10, n)) -> 
  srdbv4_count

sitemap <- sitemap +
  geom_point(data = srdbv4_count, aes(x = srdbv4_count$Longitude, y = srdbv4_count$Latitude), 
               color = "black", shape = 1, size = srdbv4_count$n2, alpha = 0.5)

# Task 1: add new points
srdbv4 %>% select(Contributor) %>% unique()
srdbv4 %>% filter(Contributor == "MH") ->
  srdb_MH

sitemap <- sitemap +
  geom_point(data = srdb_MH, aes(x = srdb_MH$Longitude, y = srdb_MH$Latitude), 
               color = "red", shape = 16, size = 3, alpha = 0.25)

# add JM points

# add DP points

sitemap
```



## representative analysis
```{r, fig.height=8, fig.width=8}
representative(srdbv4, IGBP, GlobalMATMAP) %>% 
  filter(!is.na(Ecosystem) & !is.na(MAT)) %>% 
  ggplot(aes(x = Ecosystem, y = MAT, fill = factor(Source))) +
  # geom_violin(draw_quantiles = c(0.5))
  geom_boxplot(outlier.shape = 1, outlier.color = "gray", outlier.size = 0.5) +
  labs(x=expression(Ecosystem~types), y=expression(MAT~(degree~C))) -> v4_plot

# Task 2
representative(srdbv5, IGBP, GlobalMATMAP) %>% 
  filter(!is.na(Ecosystem) & !is.na(MAT)) %>% 
  ggplot(aes(x = Ecosystem, y = MAT, fill = factor(Source))) +
  # geom_violin(draw_quantiles = c(0.5))
  geom_boxplot(outlier.shape = 1, outlier.color = "gray", outlier.size = 0.5) +
  labs(x=expression(Ecosystem~types), y=expression(MAT~(degree~C))) -> v5_plot

# use cowplot put them together
plot_grid(v4_plot, v5_plot, ncol = 1)

```


# Data check 
## Check Site_ID
```{r check Site_ID}
# check there are no lower case character in Site_ID column for bother srdb and MGRsD
MGRsD %>% 
  select (Study_number, Site_ID) %>% 
  filter (Site_ID %in% letters )

srdbv5 %>% 
  select (Study_number, Site_ID) %>% 
  filter (Site_ID %in% letters )
```


## Find out those studies in MGRsD but not in SRDB
```{r}
# 14 studies not in srdb, need to add the information
mgrsd_notin_srdb(srdbv5, MGRsD) 
```

## Find out those studies in SRDB but not in MGRsD
```{r, results = 'hide' }
srdb_notin_mgrsd(srdbv5, MGRsD) %>% 
  arrange(Study_number) %>% 
  unique()
```



## Check all countries and whether they have currect acronym
```{r}
srdbv5 %>% 
  mutate(Country_acronym = substr(Site_ID, 1,2)) %>% 
  select (Country) %>% 
  unique() %>% 
  count(Country, sort = TRUE)
```

## check country code
```{r}
MGRsD %>% 
  mutate(Country_acronym = substr(Site_ID, 1, 2)) %>% 
  select (Country, Country_acronym) %>% 
  unique() %>% 
  count(Country, Country_acronym, sort = TRUE)
```


## Find out those Site_ID in MGRsD but not in SRDB 
```{r}
site_ID_check(srdbv5) %>% 
  filter(is.na(srdb_ID)) %>% 
  filter(Study_number %!in% mgrsd_notin_srdb(srdbv5, MGRsD)[,1]) 

```

## For those have more than 11 months Rs from MGRsD, comparing that with SRDB
```{r}
# Select sites with more than 10 months' Rs measurement, and get the mean
srdb_vs_mgrsd <- function () {
  MGRsD %>% select(Study_number, Site_ID, Meas_Month, Rs_Norm) %>% 
  group_by(Study_number, Site_ID, Meas_Month) %>% 
  summarise(RS_mean = mean(Rs_Norm)) %>% 
  mutate(n_Month = n()) %>% 
  filter(n_Month >= 10) %>% 
  group_by(Study_number, Site_ID) %>% 
  summarise(RS_annual_mgrsd = mean(RS_mean)) -> 
    mgrsd_sum

# Select sites and get the mean Rs value from srdb data
  srdbv5 %>% 
    select(Study_number, Site_ID, Rs_annual) %>% 
    na.omit() %>% 
  group_by(Study_number, Site_ID) %>% 
  summarise(RS_annual_srdb = mean(Rs_annual)/365) -> 
    srdb_sum

# use inner join to combine Rs from srdb and mgrsd  
  results <- inner_join(mgrsd_sum, srdb_sum, by=c("Study_number", "Site_ID"))
  return(results)
}

srdb_vs_mgrsd <- srdb_vs_mgrsd()
```



## Regression between Rs_annual from SRDB and Rs_annual from MGRsD
```{r}
srdb_vs_mgrsd %>% 
  ggplot(aes(RS_annual_mgrsd, RS_annual_srdb)) + 
  geom_point() + 
  geom_smooth(method = "lm") +
  geom_abline(slope = 1, intercept = 0, col = "red", linetype = "dashed", size = 1.5) +
  labs(x=expression(Annual~R[S]~"(MGRsD)"), y=expression(Annual~R[S]~"(SRDB)"))

lm(RS_annual_srdb ~ RS_annual_mgrsd, data = srdb_vs_mgrsd) %>% summary()
```


## Find out sites with big Rs_annual difference between SRDB and MGRsD
```{r}
srdb_vs_mgrsd %>% 
  mutate(ratio = RS_annual_mgrsd / RS_annual_srdb) %>% 
  arrange(ratio)
```


## Check sites by contry (check latitude and longitude)
```{r}
srdbv5 %>% count(Country, sort = TRUE) 
```


## Check sites by country
```{r}
lot_long_check(srdbv5, "USA")
# srdbv5 %>% filter(Longitude > 0) %>% select(Study_number) %>% unique()
lot_long_check(srdbv5, "China")
srdbv5 %>% filter(Latitude < 22 & Country == "China") %>% 
  select(Study_number, Country, Region, Latitude, Longitude) %>% 
  arrange(Latitude)

lot_long_check(srdbv5, "Canada")
lot_long_check(srdbv5, "Finland")
lot_long_check(srdbv5, "Japan")
lot_long_check(srdbv5, "Germany")
```

## Check latitude and longitude in MGRsD but not in srdb, then srdb's lat and long can use that from MGRsD
```{r}
# srdbv5 %>% filter(is.na(Site_ID)) %>% nrow()
# lat_long_check2 <- function () {
#   srdbv5 %>% filter(is.na(Latitude) | is.na(Longitude)) %>% select(Study_number) %>% unique() %>% arrange(Study_number) -> srdb
#   MGRsD %>% select(Study_number, Latitude, Longitude) %>% unique() -> mgrsd
#   
#   results <- left_join(srdb, mgrsd, by = c("Study_number"))
#   return(results)
# }
# 
# lat_long_check2() %>% na.omit()

```


## check manipulation etc.
```{r}
srdbv5 %>% 
  count(Manipulation, sort = TRUE) 
srdbv5 %>% 
  select(Manipulation) %>% 
  unique() %>% 
  arrange(Manipulation) -> 
  manipltion
manipltion 

writ_file(manipltion, 'manipulation.csv')

srdbv5 %>% 
  count(Meas_method, sort = TRUE) 
srdbv5 %>% 
  count(Partition_method, sort = TRUE) 

# questions
srdbv5 %>% 
  count(Biome, sort = TRUE) 
srdbv5 %>% 
  count(Ecosystem_state, sort = TRUE) 
srdbv5 %>% 
  count(Leaf_habit, sort = TRUE) 
srdbv5 %>% 
  count(Stage, sort = TRUE) 
```






